A Survey on Ordered Binary Decision Diagrams

### 2015-09-13 paper.tex
Fix consistent ITE formatting

This would result in an algorithm having a worst case time complexity of 
$O\left(|V_{f_1}|^2 \cdot |V_{f_2}|^2\right)$. Therefore, Bryant~\cite{BRYANT86}
already proposed to extend the \textit{Apply} operation to support ternary
operations and then use the equivalent \textit{if-then-else} (\textit{ITE})
representation:
\begin{center}
$
ITE\left(f_2, f_1|_{x_i=1}, f_1|_{x_i=0}\right) \equiv
f_2 \land f_1|_{x_i=1} \lor \overline{f_2} \land f_1|_{x_i=0}
$
\end{center}

\noindent
For a given node $x$, the ITE operator for three nodes, \newline
$ITE(x, hi(x), lo(x))$, chooses $hi(x)$ if $x$ evaluates to true and $lo(x)$
otherwise. Computing $ITE(x, hi(x), lo(x))$ is accomplished by utilizing a
recursive formulation~\cite{BRACE90}. To shorten the recursive formula, $l$ and
$h$ are used to represent $lo(x)$ and $hi(x)$, respectively.
\begin{center}
$
ITE(x, h, l) =
(var(x), ITE(x|_{x=1}, h|_{x=1}, l|_{x=1}), ITE(x|_{x=0}, h|_{x=0}, l|_{x=0}))
$
\end{center}

@@

The time complexity then improves to be
$O\left(|V_{f_1}|^2 \cdot |V_{f_2}|\right)$~\cite{BRYANT86} when using the ITE
operator.~\cite[p. 686]{BRYANT86} lists Bryant's full pseudocode.

@@

Hence, the following sections cover important aspects to keep in mind when
implementing an OBDD framework efficiently, i.e. efficient data structures, the
ITE operator, how to possibly approach the variable ordering problem and
\textit{garbage collection}. \tbr

@@

There exists a special version of hash tables, so-called
\textit{hash-based caches}, which do not resolve collisions, i.e. overwrite
existing entries, and issue a cache miss if a looked up element is not found.
As will be seen, \textit{Hash-based caches} are useful to provide an efficient
implementation of the ITE operator. \tbr

@@

Accoring to Brace et al.~\cite{BRACE90}, the ITE operator forms the core of an
efficient OBDD package implementation. \tbr

>>>>

This would result in an algorithm having a worst case time complexity of 
$O\left(|V_{f_1}|^2 \cdot |V_{f_2}|^2\right)$. Therefore, Bryant~\cite{BRYANT86}
already proposed to extend the \textit{Apply} operation to support ternary
operations and then use the equivalent \textit{if-then-else} ($ITE$)
representation:
\begin{center}
$
ITE\left(f_2, f_1|_{x_i=1}, f_1|_{x_i=0}\right) \equiv
f_2 \land f_1|_{x_i=1} \lor \overline{f_2} \land f_1|_{x_i=0}
$
\end{center}

\noindent
For a given node $x$, the $ITE$ operator for three nodes, \newline
$ITE(x, hi(x), lo(x))$, chooses $hi(x)$ if $x$ evaluates to true and $lo(x)$
otherwise. Computing $ITE(x, hi(x), lo(x))$ is accomplished by utilizing a
recursive formulation~\cite{BRACE90}. To shorten the recursive formula, $l$ and
$h$ are used to represent $lo(x)$ and $hi(x)$, respectively.
\begin{center}
$
ITE(x, h, l) =
(var(x), ITE(x|_{x=1}, h|_{x=1}, l|_{x=1}), ITE(x|_{x=0}, h|_{x=0}, l|_{x=0}))
$
\end{center}

@@

The time complexity then improves to be
$O\left(|V_{f_1}|^2 \cdot |V_{f_2}|\right)$~\cite{BRYANT86} when using the $ITE$
operator.~\cite[p. 686]{BRYANT86} lists Bryant's full pseudocode.

@@

Hence, the following sections cover important aspects to keep in mind when
implementing an OBDD framework efficiently, i.e. efficient data structures, the
$ITE$ operator, how to possibly approach the variable ordering problem and
\textit{garbage collection}. \tbr

@@

There exists a special version of hash tables, so-called
\textit{hash-based caches}, which do not resolve collisions, i.e. overwrite
existing entries, and issue a cache miss if a looked up element is not found.
As will be seen, \textit{Hash-based caches} are useful to provide an efficient
implementation of the $ITE$ operator. \tbr

@@

Accoring to Brace et al.~\cite{BRACE90}, the $ITE$ operator forms the core of an
efficient OBDD package implementation. \tbr
